Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

Using a $3D$ domain, the difference between a flow instability and the preferential flow path that may include smaller fingers is more obvious as the latter may include finger formations. Figure \ref{fig:3DChannel_sat} describes the flow path in various instances of time showing the progression of the saturation front that now becomes more distinct. Heterogeneity is determine by the spatial distribution of porosity ($\phi =0.20$ in the current case) and permeability.

\medskip 
The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in isosurfaces shown in Fig.~\ref{fig:3DChannel_Isosurf}. However due to relatively low mesh resolution, in particular above and below the central channel region, capture of fingers (formation and growth) was very limited. In figures \ref{fig:3DChannel_sat_adapt}(a)-(f) an unstructured and adaptive mesh has been introduced in order to achieve higher resolution and focus the computational effort where is needed in he domain. For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created. At this point resolution plays an important role on capturing these patterns in detail and is also a limititation that needs to be overcome.

>>>>

The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in isosurfaces shown in Fig.~\ref{fig:3DChannel_Isosurf}. However, due to relatively low mesh resolution, in particular above and below the central channel region, capture of fingers (formation and growth) was very limited. A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using an adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}, with resolution ranging from XX to XX tetrahedral \PNDG[1]{1} element-pairs. Distinct preferable flow pathways are shown  For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created. At this point resolution plays an important role on capturing these patterns in detail and is also a limititation that needs to be overcome.

In figures \ref{fig:3DChannel_sat_adapt}(a)-(f) an unstructured and adaptive mesh has been introduced in order to achieve higher resolution and focus the computational effort where is needed in he domain. For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created. At this point resolution plays an important role on capturing these patterns in detail and is also a limititation that needs to be overcome.
